---
title: "RSM Fit"
output: html_document
  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load data

```{r load-data}
library(rsm)

design <- read.csv("/home/nasia/wine-innovation-engine/results/phase3_doe/design_matrix.csv")
head(design)
str(design)
```

Fix the strings in `reached_dryness` and `reached_practical_end` to boolean.

```{r fix-types}
design$reached_dryness <- as.logical(design$reached_dryness)
design$reached_practical_end <- as.logical(design$reached_practical_end)
```

## Responses: time, peak_rate, and conversion as a constraint (>0.99)

Mention how the coded are connected to the not coded, and clean the column
with the coded values from Python.

```{r coded-data}
design_clean <- design[, !(names(design) %in% c("x1", "x2", "x3"))]

design_coded <- coded.data(design_clean,
                            x1 ~ (Ti - 21) / 6,
                            x2 ~ (Sub0 - 265) / 15,
                            x3 ~ (N0 - 240) / 100
)
```

## Fit for peak rate

We fit a second-order model that makes 9 linear (x1, x2, x3), 3 interactions
(x1x2, x1x3, x2x3), 3 pure quadratic (x1², x2², x3²).

```{r model-peak}
model_peak <- rsm(peak_rate ~ SO(x1, x2, x3), data = design_coded)
summary(model_peak)
```

Contour / perspective plots.

```{r contour-peak}
par(mfrow = c(1, 3))
contour(model_peak, ~x1 + x2 + x3, image = TRUE)
```

It freezes at Substrate=265, we took only x1 and x3 because these
interactions are important. We add the real points.

```{r contour-peak-slice}
contour(model_peak, x1 ~ x3, at = list(x2 = -1), image = TRUE)
points(design_coded$x1, design_coded$x3, pch = 19)
```

Persp plot 3d.

```{r persp-peak}
persp(model_peak, x1 ~ x3, at = list(x2 = -1), col = terrain.colors(50), contours = "colors")
```

## Fit for time

```{r model-time}
model_time <- rsm(time ~ SO(x1, x2, x3), data = design_coded)
summary(model_time)
```

Contour / perspective plots.

```{r contour-time}
par(mfrow = c(1, 3))
contour(model_time, ~x1 + x2 + x3, image = TRUE)
```

## Fit for conversion

```{r model-conversion}
model_conversion <- rsm(conversion ~ SO(x1, x2, x3), data = design_coded)
summary(model_conversion)
```

Contour / perspective plots.

```{r contour-conversion}
par(mfrow = c(1, 3))
contour(model_conversion, ~x1 + x2 + x3, image = TRUE)
```

## Fit for ethanol

```{r model-ethanol}
model_ethanol <- rsm(ethanol ~ SO(x1, x2, x3), data = design_coded)
summary(model_ethanol)
```

Contour / perspective plots.

```{r contour-ethanol}
par(mfrow = c(1, 3))
contour(model_ethanol, ~x1 + x2 + x3, image = TRUE)
```

Because peak_rate and time have no internal optimum (stationary points out of range), the
optimum will be found on the border of the cube. In optim() we use method='L-BFGS-B' with
explicitly lower=c(-1,-1,-1) , upper=c(1,1,1) — otherwise the optimizer will suggest combinations
outside the experimental range (like −85°C).
